\input{title.tex}

### 2025-02-11 docs/papers/01_manuscript/tab_rmse.tex
fix(project): :pencil2: Fix typo in paper for thesis

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[!htbp]\footnotesize
	\centering
	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
	  \toprule
			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
	  \midrule
	  Qinghai & 5.26  & =     & FALSE & 5.89  & >     & TRUE \\
	  Gansu & 10.37  & >     & TRUE  & 9.55  & >     & TRUE \\
	  Ningxia & 5.81  & =     & FALSE & 6.83  & >     & TRUE \\
	  Inner Mongolia & 7.11  & >     & TRUE  & 1.60  & <     & TRUE \\
	  Shanxi & 1.72  & <     & TRUE  & 5.60  & >     & TRUE \\
	  Shaanxi & 3.05  & <     & TRUE  & 3.01  & >     & TRUE \\
	  Henan & 20.66  & >     & TRUE  & 1.18  & <     & TRUE \\
	  Shandong & 4.54  & =     & FALSE & 4.14  & >     & TRUE \\
	  \bottomrule
	  \end{tabularx}%
	\label{tab:addlabel}%
\end{table}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[!htbp]\footnotesize
	\centering
	\caption{Pre and post treatment root mean squared prediction error (RMSE) for YRB's provinces}\label{tab:DSC_summary}
	\begin{tabularx}{0.8\textwidth}{XXXXXXX}
	  \toprule
			& \multicolumn{3}{c}{87-WAS} & \multicolumn{3}{c}{98-UBR} \\
  \cmidrule{2-7}    province  & \multicolumn{1}{c}{post/pre} & To avg. & \multicolumn{1}{c}{sig.} & \multicolumn{1}{c}{post/pre} & To avg.   & \multicolumn{1}{c}{sig.} \\
	  \midrule
	  Qinghai & 5.26  & $=$     & FALSE & 5.89  & $>$     & TRUE \\
	  Gansu & 10.37  & $>$     & TRUE  & 9.55  & $>$     & TRUE \\
	  Ningxia & 5.81  & $=$     & FALSE & 6.83  & $>$     & TRUE \\
	  Inner Mongolia & 7.11  & $>$     & TRUE  & 1.60  & $<$     & TRUE \\
	  Shanxi & 1.72  & $<$     & TRUE  & 5.60  & $>$     & TRUE \\
	  Shaanxi & 3.05  & $<$     & TRUE  & 3.01  & $>$     & TRUE \\
	  Henan & 20.66  & $>$     & TRUE  & 1.18  & $<$     & TRUE \\
	  Shandong & 4.54  & $=$     & FALSE & 4.14  & $>$     & TRUE \\
	  \bottomrule
	  \end{tabularx}%
	\label{tab:addlabel}%
\end{table}%

### 2025-02-11 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :pencil2: Fix typo in paper for thesis

\RC{} Is $k = T x D$ or $T_0 x D$? Currently, it is stated that ``$k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset.'' However, this portion of the method focuses on the PRE-TREATMENT characteristics, shouldn't we use only the data from the PRE-TREATMENT period, i.e., $T_0$ years? As such, shouldn't $k$ be ``the product of $T_0$ and $D$, the number of pre-treatment years and dimensions''?

@@

\begin{quote}
    $\dots$ where $k$ is the product of $T_0$ and $D$, the number of pre-treatment years and dimensions in the dataset ($D = 5$ in this case).
\end{quote}

@@

\begin{quote}
    $\mathbf{X_1}$ is a ($k \times 1$) vector containing the pre-treatment average of each dimension in the dataset for the treated unit $\dots$
\end{quote}

@@

\begin{quote}
    where $\mathbf{Z}_{1}$ is a ($T_0 \times 1$) vector containing every observation of the water use for the treated unit $\dots$
\end{quote}

>>>>

\RC{} Is $k = T \times D$ or $T_0 \times D$? Currently, it is stated that ``$k$ is the product of $T$ and $D$, the number of years and dimensions in the dataset.'' However, this portion of the method focuses on the PRE-TREATMENT characteristics, shouldn't we use only the data from the PRE-TREATMENT period, i.e., $T_0$ years? As such, shouldn't $k$ be ``the product of $T_0$ and $D$, the number of pre-treatment years and dimensions''?

@@

\begin{quote}[page=7, sline=144, eline=145]
    $\dots$ where $k$ is the product of $T_0$ and $D$, the number of pre-treatment years and dimensions in the dataset ($D = 5$ in this case).
\end{quote}

@@

\begin{quote}[page=7, sline=150, eline=151]
    $\mathbf{X_1}$ is a ($k \times 1$) vector containing the pre-treatment average of each dimension in the dataset for the treated unit $\dots$
\end{quote}

@@

\begin{quote}[page=7, sline=155, eline=156]
    where $\mathbf{Z}_{1}$ is a ($T_0 \times 1$) vector containing every observation of the water use for the treated unit $\dots$
\end{quote}
